Reproducible, flexible and high throughput data extraction from primary literature: The \pkg{metaDigitise} \proglang{R} package

### 2017-11-20 docs/manuscript.tex
manuscript updates

\subsubsection{Histograms}
\fct{metaDigitise} prompts the user to enter groups names and then to click on the top corners of each bar. bars can subsequently be deleted. \fct{metaDigitise} then calculates the midpoint and the frequency for each bar.

>>>>

\subsection{Histograms}
\fct{metaDigitise} prompts the user to click on the top corners of each bar. Bars can subsequently be deleted. 
For each bar a midpoint (mean x coordinates) and a frequency (mean y coordinates, rounded to the nearest integer) is calculated. The sample size is calculated as the sum of the frequencies., the mean as
\begin{equation}
\sigma = SE * \sqrt{n}
\end{equation}
and from 95\% confidence intervals as
\begin{equation}
\sigma = \frac{CI}{1.96} * \sqrt{n}
\end{equation}

Using the x coordinates, \fct{metaDigitise} then calculates the midpoint and the frequency for each bar.
